On exponential sums arising from the classical doubling method

### 2025-03-28 main.tex
Adding a table of contents and minor chages
added one comment
Nicer notation

%% frequently used symbols
% Common math notions
\newcommand{\zIntegers}{\mathbb{Z}}
\newcommand{\rReal}{\mathbb{R}}
\newcommand{\cComplex}{\mathbb{C}}
\newcommand{\multiplicativegroup}[1]{#1^{\times}}
\newcommand{\RealPart}{\mathrm{Re}}
\newcommand{\detQuadratic}{{\det}_{\quadraticExtension}}
\newcommand{\Hom}{\mathrm{Hom}}
\newcommand{\EndomorphismRing}{\operatorname{End}}
\newcommand{\Span}{\mathrm{span}}
\newcommand{\Supp}{\mathrm{supp}}
\newcommand{\Stab}{\mathrm{stab}}
\newcommand{\idmap}{\mathrm{id}}
\newcommand{\conjugate}[1]{\overline{#1}}
\newcommand{\indicatorFunction}[1]{\delta_{#1}}
\newcommand{\isomorphic}{\cong}
\newcommand{\lengthof}{\ell}
\newcommand{\abs}[1]{\left|#1\right|}
\newcommand{\sizeof}[1]{\left|#1\right|}
\newcommand{\lcm}{\operatorname{lcm}}
\newcommand{\hermitianSpace}{\mathrm{V}}
\newcommand{\xIsotropic}{\mathrm{X}}
\newcommand{\yIsotropic}{\mathrm{Y}}
\newcommand{\similitudeCharacter}{\operatorname{sim}}

@@

@@

@@

\begin{enumerate}
    \item Unitary groups: The Weyl group $W\left(\algebraicGroup{\UnitaryGroup}_n\right)$ is isomorphic to the symmetric group $\SymmetricGroup_n$. If $\dot{w} \in \algebraicGroup{\UnitaryGroup}_n$ is a lift of $w \in W\left(\algebraicGroup{\UnitaryGroup}_n\right)$, the map $w \mapsto \dot{w} \cdot w_n$ sends a $w_n$-twisted $\SymmetricGroup_n$ conjugacy class to a $\SymmetricGroup_n$ conjugacy class. Thus twisted conjugacy classes are determined by the cycle partition $\lambda \vdash n$ associated to $\dot{w} \cdot w_n$. Let us denote by $\lambda^+$ the partition formed by taking the even parts of $\lambda$ and by $\lambda^{-}$ the partition formed by taking the odd parts of $\lambda$. The corresponding algebraic torus is
	$$^{L^{-1}w}\algebraicGroup{T}_0 \cong \prod_{i} 	\restrictionOfScalars{\finiteFieldExtension{\lambda^{+}_i}}{\finiteField}{\multiplcativeScheme} \times \prod_{i} \\
	\restrictionOfScalars{\finiteFieldExtension{\lambda_i^{-}}}{\finiteField}{\algebraicGroup{\UnitaryGroup}_1}.$$
	% The embedding into the unitary group requires conjugation by \diag(1,1,1,\sqrt{d},\sqrt{d},\sqrt{d}). I would rather not write it.

	%The embedding into $\algebraicGroup{\UnitaryGroup}_n$ is given by the map %\begin{equation}\label{eq:torus-embedding-unitary-group}
	%	\left( \left(g_i\right)_{i=1}^{\lengthof\left(\lambda^+\right)}, \left(h_i\right)_{i=1}^{\lengthof\left(\lambda^-\right)}\right) \mapsto \diag(g_1,\dots, g_{\lengthof\left(\lambda^+\right)}, h_1^{\ast}, \dots, h_{\lengthof\left(\lambda^{-}\right)}^{\ast}, \involution{(g^{\ast}_{\lengthof\left(\lambda^+\right)})}, \dots, \involution{(g^{\ast}_1)}).
	%\end{equation}
	See also \cite[Section 2.3]{ThiemVinroot2009} and \cite[Section 2.2]{SaitoShinoda2000}.
    \item (Odd special orthogonal and symplectic groups)
    For $\algebraicGroup{\Sp}_{2n}$ or $\algebraicGroup{\SO}_{2n+1}$, the Weyl group is isomorphic to $$\left\{\pm 1\right\}^n \rtimes \SymmetricGroup_n,$$ which we can identify with the group signed permutations. The conjugacy classes of the Weyl group are classified by pairs of partitions $(\lambda^+,\lambda^-)$ with $\sizeof{\lambda^+} + \sizeof{\lambda^-} = n$. See \cite[Section 2.2]{KonvalinkaMatjavPfeiffer2011} for more details. Let $(\lambda^+,\lambda^-)$ correspond to the conjugacy class of $w$ in the Weyl group. Then
		$$^{L^{-1}w}\algebraicGroup{T}_0 \cong \prod_{j} \restrictionOfScalars{\finiteFieldExtension{\lambda^+_j}}{\finiteField}{\multiplcativeScheme} \times \prod_{i} \restrictionOfScalars{\finiteFieldExtension{\lambda^-_i}}{\finiteField}{\algebraicGroup{\UnitaryGroup}_1}.$$
		See also \cite[Section 3.2 Part (B)]{Zalesski2018}.
        \item (Even special orthogonal groups) The Weyl group of $\algebraicGroup{SO}_{2n}^{\pm}$ is isomorphic to $$\left\{ \left(x_1,\dots,x_n\right) \in \left\{\pm 1\right\}^n \mid \prod_{i=1}^n x_i = 1\right\} \rtimes \SymmetricGroup_n,$$ which can be realized the subgroup of the group of signed permutations, consisting of all even signed permutations. Using this realization, we may attach to $w$ in the Weyl group a pair of partitions $\left(\lambda^+, \lambda^-\right)$ as before, with $\sizeof{\lambda^+} + \sizeof{\lambda^-} = n$. If $\lambda^{-}$ is not the empty partition, the pair $\left(\lambda^+, \lambda^-\right)$ determines the conjugacy class of $w$. Otherwise, there are two different conjugacy classes of the Weyl group corresponding to the same pair $\left(\lambda^{+}, \lambda^{-}\right)$. These two conjugacy class correspond to isomorphic tori, and these tori are not conjugate in $\algebraicGroup{\SO}_{2n}^{\pm}$. See \cite[Section 2.3]{KonvalinkaMatjavPfeiffer2011} for more details.
        \begin{enumerate}
        	\item (Split case): For $\algebraicGroup{\SO}_{2n}^+$ we have that
        	$$^{L^{-1}w}\algebraicGroup{T}_0 = \prod_{j} \restrictionOfScalars{\finiteFieldExtension{\lambda^+_j}}{\finiteField}{\multiplcativeScheme} \times \prod_{i} \restrictionOfScalars{\finiteFieldExtension{\lambda^-_i}}{\finiteField}{\algebraicGroup{\UnitaryGroup}_1}.$$
			See also \cite[Section 3.2 Parts (C) and (D)]{Zalesski2018}.        	
        	\item (Non-split case): As in the unitary group case, for $\algebraicGroup{SO}_{2n}^-$, the map $w \mapsto \dot{w}\circ (-n,n)$ sends a $(-n,n)$-twisted conjugacy class in the even signed permutation group to a conjugacy class in the signed permutation group. Let $(\lambda^+,\lambda^-)$ correspond to the signed permutation group conjugacy class of $\dot{w} \circ (-n,n)$. Then
        	$$^{L^{-1}w}\algebraicGroup{T}_0 = \prod_{j} \restrictionOfScalars{\finiteFieldExtension{\lambda^+_j}}{\finiteField}{\multiplcativeScheme} \times \prod_{i} \restrictionOfScalars{\finiteFieldExtension{\lambda^-_i}}{\finiteField}{\algebraicGroup{\UnitaryGroup}_1}.$$
			See also \cite[Section 3.2 Part (D)]{Zalesski2018}. Notice that we differ from that \cite{Zalesski2018} since we do not incorporate the element $\left(-n, n\right)$ in the Frobenius root.
        \end{enumerate}
    \end{enumerate}
	We summarize all these cases in the following theorem.

	\begin{theorem}
		A maximal rational torus $\algebraicGroup{T}$ of $\algebraicGroup{G} = \algebraicGroup{\UnitaryGroup}_{n}, \algebraicGroup{\Sp}_{2n}, \algebraicGroup{\SO}_{2n + 1}, \algebraicGroup{\SO}_{2n}^{\pm}$ is isomorphic to $$\algebraicGroup{T} \cong \prod_{j} \restrictionOfScalars{\finiteFieldExtension{\lambda^+_j}}{\finiteField}{\multiplcativeScheme} \times \prod_{i} \restrictionOfScalars{\finiteFieldExtension{\lambda^-_i}}{\finiteField}{\algebraicGroup{\UnitaryGroup}_1},$$
		where $\left(\lambda^+, \lambda^-\right)$ is a pair of partitions such that $\sizeof{\lambda^+} + \sizeof{\lambda^-} = n$, where in the unitary group case we require that $\lambda^+$ consists only of even parts and that $\lambda^-$ consists only of odd parts. We have that $$\algebraicGroup{T}^{\Frobenius} \cong \prod_{j} \multiplicativegroup{\finiteFieldExtension{\lambda_j^+}} \times \prod_{i} \NormOneGroup{2 \lambda_i^{-}}.$$ The embedding $\algebraicGroup{T}^{\Frobenius} \to \algebraicGroup{G}^{\Frobenius}$ is of the form $$\left(\left(a_j\right)_{j=1}^{\lengthof\left(\lambda^+\right)}, \left(t_i\right)_{i=1}^{\lengthof\left(\lambda^-\right)}\right) \mapsto
		\begin{pmatrix}
			\iota_+\left( \left(a_j\right)_{j=1}^{\lengthof\left(\lambda^+\right)}\right)\\
			& \iota_{-}\left( \left(t_i\right)_{i=1}^{\lengthof\left(\lambda^-\right)}
			 \right) &\\
			 & & \involution{\iota_+^{\ast}\left( \left(a_j\right)_{j=1}^{\lengthof\left(\lambda^+\right)}\right)}
		\end{pmatrix},$$
		where $\iota_+ \colon \prod_{j} \multiplicativegroup{\finiteFieldExtension{\lambda_j^+}} \to \GL_{\frac{\sizeof{\lambda^+}}{\grpIndex{\quadraticExtension}{\finiteField}}}\left(\quadraticExtension\right)$ and $\iota_- \colon \prod_{i} \NormOneGroup{2 \lambda_j^-} \to G'$ are embeddings. Here, $G'$ is a group of the same type as $\algebraicGroup{G}^{\Frobenius}$, with $n$ replaced by $\sizeof{\lambda^{-}}$.

@@

    In addition, we write the tori classification for the similitude groups we consider.
	\begin{enumerate}
		\item For $\algebraicGroup{\GSp}_{2n}$ or $\algebraicGroup{\GSO}_{2n}^+$, suppose that $(\lambda^+,\lambda^-)$ corresponds to the conjugacy class of $w$ as an element of the group of signed permutations. Then
			\begin{align*}
				^{L^{-1}w}\algebraicGroup{T}_0 \cong& \left\{\left(\left(x_j\right)_{i=1}^{\lengthof\left(\lambda^+\right)},\left(y_j\right)_{i=1}^{\lengthof\left(\lambda^-\right)},t\right) \mid \FieldNorm{2\lambda_i^-}{\lambda_i^-}(y_i) = t \text{ for every } i\right\} \\
				& \subset \prod_{i} \restrictionOfScalars{\finiteFieldExtension{\lambda^+_i}}{\finiteField}{\multiplcativeScheme} \times \prod_{i} \restrictionOfScalars{\finiteFieldExtension{2\lambda^-_i}}{\finiteField}{\multiplcativeScheme}  \times \multiplcativeScheme.
			\end{align*}
			\item For $\algebraicGroup{\GSO}_{2n}^-$, let $(\lambda^+,\lambda^-)$ correspond to the conjugacy class of $w\circ (-n,n)$ viewed as an element of the group of signed permutations. Then
			\begin{align*}
				^{L^{-1}w}\algebraicGroup{T}_0 \cong& \left\{\left(\left(x_j\right)_{i=1}^{\lengthof\left(\lambda^+\right)},\left(y_j\right)_{i=1}^{\lengthof\left(\lambda^-\right)},t\right) \mid \FieldNorm{2\lambda_i^-}{\lambda_i^-}(y_i) = t \text{ for every } i\right\} \\
				& \subset \prod_{i} \restrictionOfScalars{\finiteFieldExtension{\lambda^+_i}}{\finiteField}{\multiplcativeScheme} \times \prod_{i} \restrictionOfScalars{\finiteFieldExtension{2\lambda^-_i}}{\finiteField}{\multiplcativeScheme}  \times \multiplcativeScheme.
			\end{align*}
	\end{enumerate}

	We summarize these cases in the following theorem.
	\begin{theorem}
	A maximal rational torus $\algebraicGroup{T}$ of $\algebraicGroup{G} =  \algebraicGroup{\GSp}_{2n}, \algebraicGroup{\GSO}_{2n}^{\pm}$ is isomorphic to \begin{align*}
		\algebraicGroup{T} \cong& \left\{\left(\left(x_j\right)_{i=1}^{\lengthof\left(\lambda^+\right)},\left(y_j\right)_{i=1}^{\lengthof\left(\lambda^-\right)},t\right)  \mid \FieldNorm{2\lambda_i^-}{\lambda_i^-}(y_i) = t \text{ for every } i\right\} \\
		& \subset \prod_{i} \restrictionOfScalars{\finiteFieldExtension{\lambda^+_i}}{\finiteField}{\multiplcativeScheme} \times \prod_{i} \restrictionOfScalars{\finiteFieldExtension{2\lambda^-_i}}{\finiteField}{\multiplcativeScheme}  \times \multiplcativeScheme.
	\end{align*}
	where $\left(\lambda^+, \lambda^-\right)$ is a pair of partitions such that $\sizeof{\lambda^+} + \sizeof{\lambda^-} = n$. We have that $$\algebraicGroup{T}^{\Frobenius} \cong \left\{\left(\left(a_j\right)_{j = 1}^{\lengthof\left(\lambda^+\right)}, \left(t_i\right)_{i = 1}^{\lengthof\left(\lambda^-\right)}, z\right) \mid \FieldNorm{2 \lambda_i^{-}}{\lambda_i^{-}}\left(t_i\right) = z \text{ for all } i \right\} \subset \prod_{j} \multiplicativegroup{\finiteFieldExtension{\lambda_j^+}} \times \prod_{i} \multiplicativegroup{\finiteFieldExtension{2 \lambda_i^{-}}} \times \multiplicativegroup{\finiteField}.$$ The embedding $\algebraicGroup{T}^{\Frobenius} \to \algebraicGroup{G}^{\Frobenius}$ is of the form $$\left(\left(a_j\right)_{j=1}^{\lengthof\left(\lambda^+\right)}, \left(t_i\right)_{i=1}^{\lengthof\left(\lambda^-\right)}, z\right) \mapsto
	\begin{pmatrix}
		z \cdot \iota_+\left( \left(a_j\right)_{j=1}^{\lengthof\left(\lambda^+\right)}\right)\\
		& \iota_{-}\left( \left(t_i\right)_{i=1}^{\lengthof\left(\lambda^-\right)}, z
		\right) &\\
		& & \iota_+^{\ast}\left( \left(a_j\right)_{j=1}^{\lengthof\left(\lambda^+\right)}\right)
	\end{pmatrix},$$
	where $\iota_+ \colon \prod_{j} \multiplicativegroup{\finiteFieldExtension{\lambda_j^+}} \to \GL_{\sizeof{\lambda^+}}\left(\finiteField\right)$ and $$\iota_- \colon \left\{ \left(\left(t_i\right)_{i=1}^{\lengthof\left(\lambda^-\right)}, z\right)\in \prod_{i} \finiteFieldExtension{2\lambda^{-}_i} \times \multiplicativegroup{\finiteField} \mid \FieldNorm{2 \lambda_i^{-}}{\lambda_i^{-}}\left(t_i\right) = z \text{ for all } i \right\} \to G'$$ are embeddings. Here, $G'$ is a group of the same type as $\algebraicGroup{G}^{\Frobenius}$, with $n$ replaced by $\sizeof{\lambda^{-}}$.
\end{theorem}

@@

        0 & w

@@

For the former we will show
\[
g_{T,\rho}(\chi,\theta,\psi)= g_{T}(\chi,\theta,\psi) \cdot \begin{cases}
        1  & G \neq Sp, GSp\\
        \tau{\chi}{\psi} & G = Sp \textnormal{ or } GSp
    \end{cases}.
\]
\calvin{$\chi$ or $\chi^{-1}$? Check throughout proof!}
We will do this casewise, demonstrating in each case that the Frobeinus equivariant map $X_*(\algebraicGroup{T}) \to X_*(\algebraicGroup{G})$ decomposes into a direct sum of $\phi$'s appearing in \Cref{lem:cochar_computation}. Useful here is the description of the rational maximal tori $\algebraicGroup{T} \subseteq \algebraicGroup{G}$ and geometric Frobeinus action on $X_*(\algebraicGroup{T})$.

\GaussSumCharacter{\left(\theta'_i\right)^{-1}}{\chi^{-1}}{\fieldCharacter_{2\lambda_i^-}} 
\GaussSumCharacter{\alpha_i}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{\lambda_i^+}}} \times \GaussSumCharacter{\alpha_i^{-1}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{\lambda_i^+}}}.

>>>>

%% frequently used symbols
% Common math notions
\newcommand{\zIntegers}{\mathbb{Z}}
\newcommand{\rReal}{\mathbb{R}}
\newcommand{\cComplex}{\mathbb{C}}
\newcommand{\multiplicativegroup}[1]{#1^{\times}}
\newcommand{\RealPart}{\mathrm{Re}}
\newcommand{\detQuadratic}{{\det}_{\quadraticExtension}}
\newcommand{\Hom}{\mathrm{Hom}}
\newcommand{\EndomorphismRing}{\operatorname{End}}
\newcommand{\Span}{\mathrm{span}}
\newcommand{\Supp}{\mathrm{supp}}
\newcommand{\Stab}{\mathrm{stab}}
\newcommand{\idmap}{\mathrm{id}}
\newcommand{\conjugate}[1]{\overline{#1}}
\newcommand{\indicatorFunction}[1]{\delta_{#1}}
\newcommand{\isomorphic}{\cong}
\newcommand{\lengthof}{\ell}
\newcommand{\abs}[1]{\left|#1\right|}
\newcommand{\sizeof}[1]{\left|#1\right|}
\newcommand{\lcm}{\operatorname{lcm}}
\newcommand{\hermitianSpace}{\mathrm{V}}
\newcommand{\xIsotropic}{\mathrm{X}}
\newcommand{\yIsotropic}{\mathrm{Y}}
\newcommand{\similitudeCharacter}{\operatorname{sim}}
\newcommand{\etale}{\'etale }

@@

\tableofcontents

@@

Given a partition $\lambda = \left(\lambda_1, \dots, \lambda_\ell\right)$, we denote the \etale $\finiteField$-algebra $$\finiteFieldExtension{\lambda} = \prod_{i=1}^{\ell} \finiteFieldExtension{\lambda_i}$$ and define
$$\multiplicativegroup{\finiteFieldExtension{\lambda}} = \prod_{i=1}^{\ell} \multiplicativegroup{\finiteFieldExtension{\lambda_i}}.$$

@@

\begin{enumerate}
    \item Unitary groups: The Weyl group $W\left(\algebraicGroup{\UnitaryGroup}_n\right)$ is isomorphic to the symmetric group $\SymmetricGroup_n$. If $\dot{w} \in \algebraicGroup{\UnitaryGroup}_n$ is a lift of $w \in W\left(\algebraicGroup{\UnitaryGroup}_n\right)$, the map $w \mapsto \dot{w} \cdot w_n$ sends a $w_n$-twisted $\SymmetricGroup_n$ conjugacy class to a $\SymmetricGroup_n$ conjugacy class. Thus twisted conjugacy classes are determined by the cycle partition $\lambda \vdash n$ associated to $\dot{w} \cdot w_n$. Let us denote by $\lambda^+$ the partition formed by taking the even parts of $\lambda$ and by $\lambda^{-}$ the partition formed by taking the odd parts of $\lambda$. The corresponding algebraic torus is
	$$^{L^{-1}w}\algebraicGroup{T}_0 \cong \restrictionOfScalars{\finiteFieldExtension{\lambda^{+}}}{\finiteField}{\multiplcativeScheme} \times \restrictionOfScalars{\finiteFieldExtension{\lambda^{-}}}{\finiteField}{\algebraicGroup{\UnitaryGroup}_1}.$$
	% The embedding into the unitary group requires conjugation by \diag(1,1,1,\sqrt{d},\sqrt{d},\sqrt{d}). I would rather not write it.

	%The embedding into $\algebraicGroup{\UnitaryGroup}_n$ is given by the map %\begin{equation}\label{eq:torus-embedding-unitary-group}
	%	\left( \left(g_i\right)_{i=1}^{\lengthof\left(\lambda^+\right)}, \left(h_i\right)_{i=1}^{\lengthof\left(\lambda^-\right)}\right) \mapsto \diag(g_1,\dots, g_{\lengthof\left(\lambda^+\right)}, h_1^{\ast}, \dots, h_{\lengthof\left(\lambda^{-}\right)}^{\ast}, \involution{(g^{\ast}_{\lengthof\left(\lambda^+\right)})}, \dots, \involution{(g^{\ast}_1)}).
	%\end{equation}
	See also \cite[Section 2.3]{ThiemVinroot2009} and \cite[Section 2.2]{SaitoShinoda2000}.
    \item (Odd special orthogonal and symplectic groups)
    For $\algebraicGroup{\Sp}_{2n}$ or $\algebraicGroup{\SO}_{2n+1}$, the Weyl group is isomorphic to $$\left\{\pm 1\right\}^n \rtimes \SymmetricGroup_n,$$ which we can identify with the group signed permutations. The conjugacy classes of the Weyl group are classified by pairs of partitions $(\lambda^+,\lambda^-)$ with $\sizeof{\lambda^+} + \sizeof{\lambda^-} = n$. See \cite[Section 2.2]{KonvalinkaMatjavPfeiffer2011} for more details. Let $(\lambda^+,\lambda^-)$ correspond to the conjugacy class of $w$ in the Weyl group. Then
	$$^{L^{-1}w}\algebraicGroup{T}_0 \cong \restrictionOfScalars{\finiteFieldExtension{\lambda^{+}}}{\finiteField}{\multiplcativeScheme} \times \restrictionOfScalars{\finiteFieldExtension{\lambda^{-}}}{\finiteField}{\algebraicGroup{\UnitaryGroup}_1}.$$
		See also \cite[Section 3.2 Part (B)]{Zalesski2018}.
        \item (Even special orthogonal groups) The Weyl group of $\algebraicGroup{SO}_{2n}^{\pm}$ is isomorphic to $$\left\{ \left(x_1,\dots,x_n\right) \in \left\{\pm 1\right\}^n \mid \prod_{i=1}^n x_i = 1\right\} \rtimes \SymmetricGroup_n,$$ which can be realized the subgroup of the group of signed permutations, consisting of all even signed permutations. Using this realization, we may attach to $w$ in the Weyl group a pair of partitions $\left(\lambda^+, \lambda^-\right)$ as before, with $\sizeof{\lambda^+} + \sizeof{\lambda^-} = n$. If $\lambda^{-}$ is not the empty partition, the pair $\left(\lambda^+, \lambda^-\right)$ determines the conjugacy class of $w$. Otherwise, there are two different conjugacy classes of the Weyl group corresponding to the same pair $\left(\lambda^{+}, \lambda^{-}\right)$. These two conjugacy class correspond to isomorphic tori, and these tori are not conjugate in $\algebraicGroup{\SO}_{2n}^{\pm}$. See \cite[Section 2.3]{KonvalinkaMatjavPfeiffer2011} for more details.
        \begin{enumerate}
        	\item (Split case): For $\algebraicGroup{\SO}_{2n}^+$ we have that
        	$$^{L^{-1}w}\algebraicGroup{T}_0 \cong \restrictionOfScalars{\finiteFieldExtension{\lambda^{+}}}{\finiteField}{\multiplcativeScheme} \times \restrictionOfScalars{\finiteFieldExtension{\lambda^{-}}}{\finiteField}{\algebraicGroup{\UnitaryGroup}_1}.$$
        	See also \cite[Section 3.2 Parts (C) and (D)]{Zalesski2018}.        	
        	\item (Non-split case): As in the unitary group case, for $\algebraicGroup{SO}_{2n}^-$, the map $w \mapsto \dot{w}\circ (-n,n)$ sends a $(-n,n)$-twisted conjugacy class in the even signed permutation group to a conjugacy class in the signed permutation group. Let $(\lambda^+,\lambda^-)$ correspond to the signed permutation group conjugacy class of $\dot{w} \circ (-n,n)$. Then
        	$$^{L^{-1}w}\algebraicGroup{T}_0 \cong \restrictionOfScalars{\finiteFieldExtension{\lambda^{+}}}{\finiteField}{\multiplcativeScheme} \times \restrictionOfScalars{\finiteFieldExtension{\lambda^{-}}}{\finiteField}{\algebraicGroup{\UnitaryGroup}_1}.$$
			See also \cite[Section 3.2 Part (D)]{Zalesski2018}. Notice that we differ from that \cite{Zalesski2018} since we do not incorporate the element $\left(-n, n\right)$ in the Frobenius root.
        \end{enumerate}
    \end{enumerate}
	We summarize all these cases in the following theorem.

	\begin{theorem}
		A maximal rational torus $\algebraicGroup{T}$ of $\algebraicGroup{G} = \algebraicGroup{\UnitaryGroup}_{n}, \algebraicGroup{\Sp}_{2n}, \algebraicGroup{\SO}_{2n + 1}, \algebraicGroup{\SO}_{2n}^{\pm}$ is isomorphic to 	$$\algebraicGroup{T} \cong \restrictionOfScalars{\finiteFieldExtension{\lambda^{+}}}{\finiteField}{\multiplcativeScheme} \times \restrictionOfScalars{\finiteFieldExtension{\lambda^{-}}}{\finiteField}{\algebraicGroup{\UnitaryGroup}_1},$$
		where $\left(\lambda^+, \lambda^-\right)$ is a pair of partitions such that $\sizeof{\lambda^+} + \sizeof{\lambda^-} = n$, where in the unitary group case we require that $\lambda^+$ consists only of even parts and that $\lambda^-$ consists only of odd parts. We have that $$\algebraicGroup{T}^{\Frobenius} \cong \multiplicativegroup{\finiteFieldExtension{\lambda^+}} \times \NormOneGroup{2 \lambda^{-}}.$$ The embedding $\algebraicGroup{T}^{\Frobenius} \to \algebraicGroup{G}^{\Frobenius}$ is of the form $$\left(a, t\right) \mapsto
		\begin{pmatrix}
			\iota_+\left(a\right)\\
			& \iota_{-}\left(t\right) &\\
			 & & \involution{\iota_+^{\ast}\left(a\right)}
		\end{pmatrix},$$
		where $\iota_+ \colon \multiplicativegroup{\finiteFieldExtension{\lambda^+}} \to \GL_{\frac{\sizeof{\lambda^+}}{\grpIndex{\quadraticExtension}{\finiteField}}}\left(\quadraticExtension\right)$ and $\iota_- \colon \NormOneGroup{2 \lambda^{-}} \to G'$ are embeddings. Here, $G'$ is a group of the same type as $\algebraicGroup{G}^{\Frobenius}$, with $n$ replaced by $\sizeof{\lambda^{-}}$.

@@

    In addition, we write the tori classification for the similitude groups we consider.
	\begin{enumerate}
		\item For $\algebraicGroup{\GSp}_{2n}$ or $\algebraicGroup{\GSO}_{2n}^+$, suppose that $(\lambda^+,\lambda^-)$ corresponds to the conjugacy class of $w$ as an element of the group of signed permutations. Then
			\begin{align*}
				^{L^{-1}w}\algebraicGroup{T}_0 \cong& \left\{\left(x,y,z\right) \in  \restrictionOfScalars{\finiteFieldExtension{\lambda^+}}{\finiteField}{\multiplcativeScheme} \times \restrictionOfScalars{\finiteFieldExtension{2\lambda^-}}{\finiteField}{\multiplcativeScheme}  \times \multiplcativeScheme \mid \FieldNorm{2\lambda^-}{\lambda^-}(y) = z \right\}.
			\end{align*}
			\item For $\algebraicGroup{\GSO}_{2n}^-$, let $(\lambda^+,\lambda^-)$ correspond to the conjugacy class of $w\circ (-n,n)$ viewed as an element of the group of signed permutations. Then
			\begin{align*}
				^{L^{-1}w}\algebraicGroup{T}_0 \cong& \left\{\left(x,y,z\right) \in  \restrictionOfScalars{\finiteFieldExtension{\lambda^+}}{\finiteField}{\multiplcativeScheme} \times \restrictionOfScalars{\finiteFieldExtension{2\lambda^-}}{\finiteField}{\multiplcativeScheme}  \times \multiplcativeScheme \mid \FieldNorm{2\lambda^-}{\lambda^-}(y) = z \right\}.
			\end{align*}
	\end{enumerate}

	We summarize these cases in the following theorem.
	\begin{theorem}
	A maximal rational torus $\algebraicGroup{T}$ of $\algebraicGroup{G} =  \algebraicGroup{\GSp}_{2n}, \algebraicGroup{\GSO}_{2n}^{\pm}$ is isomorphic to \begin{align*}
				^{L^{-1}w}\algebraicGroup{T}_0 \cong& \left\{\left(x,y,z\right) \in  \restrictionOfScalars{\finiteFieldExtension{\lambda^+}}{\finiteField}{\multiplcativeScheme} \times \restrictionOfScalars{\finiteFieldExtension{2\lambda^-}}{\finiteField}{\multiplcativeScheme}  \times \multiplcativeScheme \mid \FieldNorm{2\lambda^-}{\lambda^-}(y) = z \right\}.
	\end{align*}
	where $\left(\lambda^+, \lambda^-\right)$ is a pair of partitions such that $\sizeof{\lambda^+} + \sizeof{\lambda^-} = n$. We have that $$\algebraicGroup{T}^{\Frobenius} \cong \left\{\left(x, y, z\right) \in \multiplicativegroup{\finiteFieldExtension{\lambda^+}} \times \multiplicativegroup{\finiteFieldExtension{2 \lambda^-}} \times \multiplicativegroup{\finiteField} \mid \FieldNorm{2 \lambda^{-}}{\lambda^{-}}\left(t_i\right) = z \right\}.$$ The embedding $\algebraicGroup{T}^{\Frobenius} \to \algebraicGroup{G}^{\Frobenius}$ is of the form $$\left(x, y, z\right) \mapsto
	\begin{pmatrix}
		z \cdot \iota_+ \left(x\right)\\
		& \iota_{-}\left(y\right) &\\
		& & \iota_+^{\ast}\left(x\right)
	\end{pmatrix},$$
	where $\iota_+ \colon \multiplicativegroup{\finiteFieldExtension{\lambda^+}} \to \GL_{\sizeof{\lambda^+}}\left(\finiteField\right)$ and $$\iota_- \colon \left\{ \left(y, z\right)\in \multiplicativegroup{\finiteFieldExtension{2 \lambda^-}} \times \multiplicativegroup{\finiteField} \mid \FieldNorm{2 \lambda^{-}}{\lambda^{-}}\left(y\right) = z \text{ for all } i \right\} \to G'$$ are embeddings. Here, $G'$ is a group of the same type as $\algebraicGroup{G}^{\Frobenius}$, with $n$ replaced by $\sizeof{\lambda^{-}}$.
\end{theorem}

@@

        0 & w^{\ast}

@@

For the former we will show
\[
g_{T,\rho}(\chi,\theta,\psi)= g_{T}(\chi,\theta,\psi) \cdot \begin{cases}
        1  & G \neq Sp, GSp\\
        \tau\left(\chi, \fieldCharacter\right) & G = Sp \textnormal{ or } GSp
    \end{cases}.
\]
\calvin{$\chi$ or $\chi^{-1}$? Check throughout proof!}
We will do this casewise, demonstrating in each case that the Frobeinus equivariant map $X_*(\algebraicGroup{T}) \to X_*(\algebraicGroup{G})$ decomposes into a direct sum of $\phi$'s appearing in \Cref{lem:cochar_computation}. Useful here is the description of the rational maximal tori $\algebraicGroup{T} \subseteq \algebraicGroup{G}$ and geometric Frobeinus action on $X_*(\algebraicGroup{T})$.
